### 2017-10-23 paper/sections/3_posix_overheads.tex
paper: peter edits
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% CITE ME Lustre paralle
Figure~\ref{fig:overhead-creates} shows the resource utilization of compiling
the Linux kernel.  The \texttt{untar} phase, which is characterized by many
creates, has the highest resource usage (combined CPU, network, and disk)
because of the number of RPCs needed for consistency and durability. The RPCs are
also serialized because the metadata server is single threaded; although naive,
this design is common because of the complexity of multi-threaded metadata
servers.  Traditional file system techniques for improving performance, such as
caching inodes, do not help for create-heavy workloads.

In this section, we quantify the costs of strong consistency and global
durability in CephFS. At the end of each subsection we compare the approach to
``decoupled namespaces", the technique in related work that detaches subtrees
from the global namespace to relax consistency/durability guarantees.  We use
the kernel client so that we can find the true create speed of the server; our
experiments show a low CPU utilization for the clients which indicates that we
are stressing the servers more.

@@

% - sequential IO, trim redundant operations
\textbf{CephFS Design}: a journal of metadata updates that streams into the
resilient object store. Similar to LFS~\cite{rosenblum:acm1992-LFS} and
WAFL~\cite{hitz:wtec1994-WAFL} the metadata journal is designed to grow large
(on the order of MBs) which ensures (1) sequential writes into the object store
and (2) the ability for daemons to trim redundant or irrelevant journal
entries.  The journal is striped over objects where multiple journal updates
can reside on the same object. There are two tunables for controlling the
journal: the segment size and the number of segments that can be written in
parallel. Unless the journal saturates memory or CPU resources, larger values
for these tunables results in better performance.

>>>>

% CITE ME Lustre paralle
Figure~\ref{fig:overhead-creates} shows the resource utilization of compiling
the Linux kernel.  The \texttt{untar} phase, which is characterized by many
creates, has the highest resource usage (combined CPU, network, and disk)
because of the number of RPCs needed for consistency and durability. The RPCs
are also serialized because the metadata server is single threaded; although
naive, this design is common because of the complexity of multi-threaded
metadata servers.  Traditional file system techniques for improving
performance, such as caching inodes, do not help for create-heavy workloads.
In this section, we quantify the costs of consistency and durability in CephFS.
At the end of each subsection we compare the approach to ``decoupled
namespaces", the technique in related work that detaches subtrees from the
global namespace to relax consistency/durability guarantees.

@@

% - sequential IO, trim redundant operations
\textbf{CephFS Design}: a journal of metadata updates that streams into the
resilient object store. Similar to LFS~\cite{rosenblum:acm1992-LFS} and
WAFL~\cite{hitz:wtec1994-WAFL} the metadata journal is designed to be large
(on the order of MBs) which ensures (1) sequential writes into the object store
and (2) the ability for daemons to trim redundant or irrelevant journal
entries.  The journal is striped over objects where multiple journal updates
can reside on the same object. There are two tunables for controlling the
journal: the segment size and the number of segments that can be written in
parallel. Unless the journal saturates memory or CPU resources, larger values
for these tunables results in better performance.

### 2017-10-23 paper/sections/4_methodology.tex
paper: peter edits
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% which system they represent and which are impossible
Existing, state-of-the-art systems in HPC can be represented by the cells in
Table~\ref{table:spectrum}.  POSIX IO-compliant systems like CephFS and IndexFS
have global consistency and durability~\footnote{This is the normal case.
IndexFS also has bulk merge which would transition the system into ``weak
consistency"}; DeltaFS uses ``invisible" consistency and ``local" durability
and BatchFS uses ``weak" consistency and ``local" durability. These systems
have other features that could push them into different semantics but we assign
labels here based on the points emphasized in the papers.  To compose the
mechanisms users inject which mechanisms to run and which to use in parallel
using a domain specific language.  Although we can achieve all permutations of
the different guarantees in Table~\ref{table:spectrum}, not all of them make
sense. For example, it makes little sense to do \texttt{append client
journal+RPCs} since both mechanisms do the same thing or \texttt{stream+save}
since ``global" durability is stronger and has more overhead than ``local"
durability. The cost of each mechanism and the semantics described above are
quantified in Sections~\S\ref{sec:microbenchmarks} and~\S\ref{sec:use-case-1}.

>>>>

% which system they represent and which are impossible
Existing, state-of-the-art systems in HPC can be represented by the cells in
Table~\ref{table:spectrum} (we construct the semantics for these systems later
in Section~\S\ref{sec:microbenchmarks}).  POSIX IO-compliant systems like
CephFS and IndexFS have global consistency and durability~\footnote{This is the
normal case.  IndexFS also has bulk merge which would transition the system
into ``weak consistency"}; DeltaFS uses ``invisible" consistency and ``local"
durability and BatchFS uses ``weak" consistency and ``local" durability. These
systems have other features that could push them into different semantics but
we assign labels here based on the points emphasized in the papers.  To compose
the mechanisms users inject which mechanisms to run and which to use in
parallel using a domain specific language.  Although we can achieve all
permutations of the different guarantees in Table~\ref{table:spectrum}, not all
of them make sense. For example, it makes little sense to do \texttt{append
client journal+RPCs} since both mechanisms do the same thing or
\texttt{stream+save} since ``global" durability is stronger and has more
overhead than ``local" durability. The cost of each mechanism and the semantics
described above are quantified in Sections~\S\ref{sec:microbenchmarks}
and~\S\ref{sec:use-case-1}.

### 2017-10-23 paper/sections/6_results.tex
paper: peter edits
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\textbf{Takeaway}: measuring the mechanisms individually shows that
their overheads and costs can differ {\it by orders of magnitude}. Cudele gives
users the ability to quantify the performance impact of different
consistency/durability guarantees.\\

@@

\textbf{Takeaway}: the API lets users isolate directories when applications
need better and more reliable performance. This is a way of controlling
consistency.

>>>>

\textbf{Takeaway}: measuring the mechanisms individually shows that their
overheads and costs can differ {\it by orders of magnitude}. We also show that
some mechanisms, like Nonvolatile Apply, are not worthwhile as currently
implemented.

@@

\textbf{Takeaway}: the API lets users isolate directories when applications
need better and more reliable performance. Blocking updates is an effective way of
controlling consistency.
